Reading Notes

### 2020-08-21 2pd.tex
notes from boss -- fixing objectives

%%<why do opvs matter>
The global climate crisis is one of the most pressing issue humanity faces today.
Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in Figure \ref{fig:opv} a\cite{Dou2013}.
\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref \cite{Dou2013}. Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
    \label{fig:opv}
\end{wrapfigure}
However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
    \caption{Efficiencies of all photovoltaic technologies from 1976 to present. OPVs are denoted by red filled circles. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Image taken from ref \cite{NREL2020}.}
    \label{fig:nrel}
\end{figure}

In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see Figure \ref{fig:opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, \textit{3,9-bis(2-ethylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno(2,3-d:2',3'-d')-s-indaceno(1,2-b:5,6-b')dithiophene} (\textbf{ITIC}), and a polymer donor, \textit{poly((4,8-bis((2ethylhexyl)oxy)benzo(1,2-b:4,5-b')dithiophene-2,6-diyl)(3-fluoro-2-((2-ethylhexyl)carbonyl)thieno(3,4-b)thiophenediyl))} (\textbf{PTB7}). 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.

@@

@@

\subsection*{Objective 1: Develop a coarse graining workflow}

A minimum working example of this coarse graining workflow has been completed. %% cite grits
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse grain structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse grain structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
I have made a minimum working example of an MSIBI workflow; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
although this was useful to me in getting a better understanding for the MSIBI process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
The force field obtained using MSIBI will be used to run a large CG simulation.
The end product of this first objective will be to obtain equilibrated CG trajectories.

\subsection*{Objective 2: Develop a backmapping workflow}

Given an equilibrated CG trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with addition position restraint. 
I have developed a minimum working example of this backmapping process, %% cite grits
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.

\subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}

@@

\subsection*{Objective 4: Analysis}

>>>>

%%<why do opvs matter>
The global climate crisis is one of the most pressing issue humanity faces today.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref \cite{Dou2013}. Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
    \label{fig:opv}
\end{wrapfigure}
Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{fig:opv} a\cite{Dou2013}.
However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
    \caption{Efficiencies of all photovoltaic technologies from 1976 to present. OPVs are denoted by red filled circles. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Image taken from ref \cite{NREL2020}.}
    \label{fig:nrel}
\end{figure}
%% TODO
%% opvs are vast
%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
%% what you can buy vs champion devices
%% opvs show room to grow
%% paying for themselves
%%underdog
In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see Figure \ref{fig:opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

% TODO
%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
%% look up the 17% solar cell--whats in it?
%% freedom in choosing our ingredients - can we get better than trial and error
Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.

@@

%% make better opvs
%% need to get a morphology on relevant lengthscale
%% many different chemistries
%% need a model that get a cg model from a chemistry

@@

%% Objectives are like steps along the way
%% objectives should be
% 1. goal of the step
% 2. how to do the step
% how doing this achieves the goal
%% how to coarse grain reproducibly
\subsection*{Objective 1: Develop a generalized toolset for coarse graining and performing simulations of novel molecules for organic photovoltaics}
% mapping
% ff creation
% infrastructure: porting ff to engine
In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse grain models.
This objective consists of three steps:
\begin{enumerate}
    \item {Create a tool that uses a mapping operator to go from atomistic to coarse grain structure}
    \item {Use the mapped coarse grain structure to parameterize a force field using MSIBI}
    \item {Develop the infrastructure to port this force field to a simulation engine}
\end{enumerate}
A minimum working example of this coarse grain mapping tool has been completed. %% cite grits, cg-tutorial
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse grain structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse grain structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
The force field obtained using MSIBI will then be used to run a simulation of a novel coarse grain model.
Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
The coarse graining workflow will be considered complete when it can be used to coarse grain a test set of 25 common OPV chemistried. % 25 is just in there as a random number
% workflow is complete when we can cg these chemistries
% use ff in different sim engines

\subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse grain morphology}

In order to calculate the charge transport of a coarse grain OPV system, we need to be able to regain the atomic positions.
Given an equilibrated coarse grain trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure. 
I have developed a minimum working example of this backmapping process, %% cite grits
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
The backmapping workflow will be considered complete when it can backmap a test set of 25 common OPV chemistries from all possible mappings.

\subsection*{Objective 3: Predict nanostructure of novel OPV chemistries}

@@

% predict nanostructure of new opv blends TODO new objective?
% do math -- how long will it take me to graduate? how many sims can i do?

\subsection*{Objective 4: Analysis} % calulcate mobilities compare structural properties to experiment
% identify chemical features correlated to robust mobilities
